Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2018-10-20 documentation/paper.tex
Added data table for updated waveform grid search
Included a ton and a half of citations

@@

When this extraneous information was cropped out and the architecture was modified, both accuracy and class-wise standard deviation remained quite high. The best configuration during a grid search was 96\% accurate and had a standard deviation of 0.41 (seen in Figure \ref{waveform_hist}). This is better by both metrics than the multi-layer perceptron used in the original PICO-60 analysis.

\begin{figure}[H]
    \centering
    % \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConv(\omega)$ discriminator. (Validation Event Count is the number of events in the validation set that fall within a certain network prediction band.)}
\end{figure}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConv(\omega)$ configurations.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Conv Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

The gradients produced by this technique are used for training in the same way as gradients calculated with a loss function. Backpropagation is used to calculate gradients for previous layers, and a stochastic gradient descent optimizer is used for weight updates.

@@

During a grid search of parameters of the gravitational differentiation algorithm (in addition to the stochastic gradient descent learning rate), the highest mean accuracy over three runs of an individual configuration was 99\%. The highest accuracy was obtained with 256 labeled examples in the set $\varsigma$ (out of 496 total training examples). High accuracy statistics in this range were also obtained using 128 examples (99\% accuracy, once again) and 64 examples (97\% accuracy). 32 examples produced a much lower maximum accuracy, at only 83\%. From this, it is evident that it is possible to achieve very high accuracy using this technique. It is also clear that, in general, larger initial sets produce higher performance.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Gravitational differentiation accuracy statistics by size of $\varsigma$.} \label{grav_accuracy_by_varsigma}
        \begin{tabular}{|l|l|l|}
            \hline
            Initial $\varsigma$ Size & Max Accuracy & Mean Accuracy \\
            \hline
            32 & 83\% & 69\% \\
            \hline
            64 & 97\% & 73\% \\
            \hline
            128 & 99\% & 84\% \\
            \hline
            256 & 99\% & 94\% \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Iterative cluster nucleation accuracy statistics by initial size of $\varsigma$.} \label{icn_accuracy_by_varsigma}
        \begin{tabular}{|l|l|l|}
            \hline
            Initial $\varsigma$ Size & Max Accuracy & Mean Accuracy \\
            \hline
            32 & 95\% & 75\% \\
            \hline
            64 & 97\% & 84\% \\
            \hline
            128 & 98\% & 95\% \\
            \hline
            256 & 99\% & 97\% \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

All programming for this study was done in Python 3. Keras \cite{keras}, running on a TensorFlow backend, was used for all machine learning tasks. NumPy and SciPy were used for linear algebra and signal processing. ROOT, scikit-image and scikit-learn were used for data loading and storage. Matplotlib was used for data visualization.

>>>>

For stochastic optimization of the loss function while training, the Adam \cite{adam} optimizer was used where not otherwise specified.

@@

When this extraneous information was cropped out and the architecture was modified, both accuracy and class-wise standard deviation remained quite high. The most accurate configuration during a grid search was 95\% accurate and had a standard deviation of 0.52 (seen in Figure \ref{waveform_hist}). This is better by both metrics than the multi-layer perceptron used in the original PICO-60 analysis.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{waveform_hist}
    \caption{\label{waveform_hist} Prediction distribution of the best $DeepConv(\omega)$ discriminator. (Validation Event Count is the number of events in the validation set that fall within a certain network prediction band.)}
\end{figure}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{$DeepConv(\omega)$ configurations.}
        \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
            \hline
            L2 $\lambda$ & Dropout & Filters & Kernel & Conv Layers & Max Accuracy & Precision & Recall & CWSD \\
            \hline
            0.003 & 0 & 24 & 3 & 17 & 95\% & 97\% & 97\% & 0.52 \\
            % ../experimental_data/validation_results/waveform_grid_search/l2_lambda0.003/dense_dropout0/first_layer_filters24/kernel_size3/convolutional_layers_per_group3/time1539990193_epoch57.json
            \hline
            0.003 & 0.25 & 48 & 3 & 17 & 94\% & 100\% & 91\% & 0.44 \\
            \hline
            0.001 & 0.25 & 24 & 5 & 17 & 95\% & 99\% & 94\% & 0.46 \\
            \hline
            0.001 & 0.25 & 24 & 5 & 32 & 91\% & 94\% & 94\% & 0.66 \\
            \hline
            0.0003 & 0 & 48 & 5 & 32 & 88\% & 94\% & 89\% & 0.61 \\
            \hline
            0.0003 & 0 & 24 & 3 & 17 & 93\% & 96\% & 95\% & 0.59 \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

The gradients produced by this technique are used for training in the same way as gradients calculated with a loss function. Backpropagation is used to calculate gradients for previous layers, and a stochastic gradient descent optimizer \cite{sgd} is used for weight updates.

@@

During a grid search of parameters of the gravitational differentiation algorithm (in addition to the stochastic gradient descent learning rate), the highest mean accuracy over three runs of an individual configuration was 99\%. The highest accuracy was obtained with 256 labeled examples in the set $\varsigma$ (out of 496 total training examples), which equates to 52\% of the data being labeled. High accuracy statistics in this range were also obtained using 128 examples (99\% accuracy, once again) and 64 examples (97\% accuracy). 32 examples produced a much lower maximum accuracy, at only 83\%. From this, it is evident that it is possible to achieve very high accuracy using this technique. It is also clear that, in general, larger initial sets produce higher performance.

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Gravitational differentiation accuracy statistics by size of $\varsigma$.} \label{grav_accuracy_by_varsigma}
        \begin{tabular}{|l|l|l|l|}
            \hline
            Initial $\varsigma$ Size & Proportion of Data Labeled & Max Accuracy & Mean Accuracy \\
            \hline
            32 & 6\% & 83\% & 69\% \\
            \hline
            64 & 13\% & 97\% & 73\% \\
            \hline
            128 & 26\% & 99\% & 84\% \\
            \hline
            256 & 52\% & 99\% & 94\% \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

\begin{minipage}{\textwidth}
    \begin{center}
        \captionof{table}{Iterative cluster nucleation accuracy statistics by initial size of $\varsigma$.} \label{icn_accuracy_by_varsigma}
        \begin{tabular}{|l|l|l|l|}
            \hline
            Initial $\varsigma$ Size & Proportion of Data Labeled & Max Accuracy & Mean Accuracy \\
            \hline
            32 & 6\% & 95\% & 75\% \\
            \hline
            64 & 13\% & 97\% & 84\% \\
            \hline
            128 & 26\% & 98\% & 95\% \\
            \hline
            256 & 52\% & 99\% & 97\% \\
            \hline
        \end{tabular}
    \end{center}
\end{minipage}

@@

All programming for this study was done in Python 3. Keras \cite{keras}, running on a TensorFlow backend, was used for all machine learning tasks. NumPy \cite{numpy} and SciPy \cite{scipy} were used for linear algebra and signal processing. ROOT \cite{root}, scikit-image \cite{scikit-image}, and scikit-learn \cite{scikit-learn} were used for data loading and storage. Matplotlib was used for data visualization.
